---
title: "Add more Features to Enc Data for Biostat"
output: html_document
---


```{r}
library(ini)
config <- read.ini("../../config.ini")

# set directory
working_dir <- paste(config$Directories$repos_dir, config$Directories$working_dir_suffix, sep = "/")

output_dir <- paste(config$Directories$repos_dir, config$Directories$output_dir_suffix, sep = "/")
out_root <- config$RAR$out_root

```


```{r setup, include=FALSE, cache=TRUE, root.dir=working_dir}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = working_dir)
setwd(working_dir)
source("../../common_anal/RAR_fxns.R", chdir = TRUE)

```

## Encounter
Read in raw encounter and filter out only PATIENT_MASTER_CLASS == "OUTPATIENT"
```{r load_enc, dependson=c("load_enc")}
library(dplyr)
library(data.table)
library(tibble)
suppressMessages(library(tidyr))

colClasses <- c(ENC_DATE = "PDS_DateTime", E_SOURCE_LAST_UPDATE = 'PDS_DateTime', 
                  EMPI = 'character', PK_ENCOUNTER_ID = 'character', 
                  HAR_NUMBER = 'character', PATIENT_MASTER_CLASS = 'character', ADMIT_SOURCE = 'character', 
                  ENCOUNTER_SUB_TYPE = 'character', 
                  ROLE_ADMIT = 'character', DISCIPLINE_ADMIT = 'character', ENC_TYPE_CODE = 'character', 
                  ENC_TYPE_MASTER_CODE = 'character', ENC_TYPE_MASTER_DESCRIPTION = 'character', 
                  MASTER_LOCATION_CODE = 'character', MASTER_LOCATION_DESCRIPTION = 'character', 
                  MASTER_LOCATION_FACILITY_YN = 'character', MASTER_LOCATION_CLINIC_YN = 'character',
                  MASTER_LOCATION_ENTITY = 'character', SERVICE_MASTER_CODE = 'character', 
                  SERVICE_MASTER_DESCRIPTION = 'character', 
                  BP_SYSTOLIC = 'numeric', BP_DIASTOLIC = 'numeric')
  
  
  
rar_enc <- fread_epic(dat_file = "/data/raw_data/PA/HERMANDA_RAR_PTS_ENC.csv", colClasses = colClasses, logger = NULL)


rar_enc %<>% 
      filter(PATIENT_MASTER_CLASS == "OUTPATIENT")  
nrow(rar_enc) # 2178870
```

Create new ENC ID: EMPI_DATE
```{r, dependson=c("load_enc")}
rar_enc$EMPI_DATE <- paste(rar_enc$EMPI, 
                             format(rar_enc$ENC_DATE, "%Y-%m-%d"))
length(unique(rar_enc$EMPI_DATE)) # 1298403 Unique EMPI_DATE <- Goal
```
Break rar_enc into two parts:
```{r, dependson=c("load_enc")}
dups <- unique(rar_enc[duplicated(rar_enc$EMPI_DATE), "EMPI_DATE"])

r0 <- rar_enc %>% filter(!(EMPI_DATE %in% dups$EMPI_DATE))
r1 <- rar_enc %>% filter(EMPI_DATE %in% dups$EMPI_DATE)
```

Deal with r1
```{r, dependson=c("load_enc")}
length(unique(r1$ENC_TYPE_MASTER_CODE)) # 133
table(r1$ENC_TYPE_MASTER_DESCRIPTION)
```

Factorize part of ENC_TYPE_MASTER_CODE (Not perfect)
```{r, dependson=c("load_enc")}
r1$ENC_TYPE_MASTER_CODE <- factor(r1$ENC_TYPE_MASTER_CODE, levels = c("OFFICE VISIT", "LAB","SURGERY", "DAY SURG", "SURGERY, GENERAL","APPOINTMENT","ORDERS","CONSULT", "FORMS","LETTER","PHONE","SCAN - OLD RECORDS","HISTORY"))

temp <- r1 %>% 
      group_by(EMPI_DATE) %>%
      arrange(ENC_TYPE_MASTER_CODE, desc(E_SOURCE_LAST_UPDATE)) %>%
      mutate_at(vars(BP_SYSTOLIC:BP_DIASTOLIC), 
                funs(median(., na.rm = FALSE))) %>%
      slice(1) %>%
      ungroup()
length(unique(temp$ENC_DATE)) # 454554
table(temp$ENC_TYPE_MASTER_CODE)
```
It seems that the specified 13 groups could distinguish all, unless some levels are needed inside this order.




## Dx's
Dx's for Obstructive Sleep Apnea
```{r load_Dx, dependson=c("load_Dx")}
rar_dx <- load_RAR_Dx()

osa_9 <- rar_dx[grepl("^327.2", rar_dx$CODE), "CODE"]
table(osa_9$CODE)

```
Additional?
```{r, dependson=c("load_Dx")}
osa_9a <- rar_dx[grepl("^780.5", rar_dx$CODE), "CODE"]
table(osa_9a$CODE)
```




```{r, dependson=c("load_Dx")}
osa_10 <- rar_dx[grepl("G47.3", rar_dx$CODE), "CODE"]
table(osa_10$CODE)
```

Dx for Diabetes
```{r, dependson=c("load_Dx")}
diabetes_9 <- rar_dx[grepl("^250", rar_dx$CODE), "CODE"]
table(diabetes_9$CODE)
```

