---
title: "Time Cutpoint - v0.2"
output: 
  html_document:
    fig_width: 20
    fig_height: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, autodep=TRUE)

knitr::opts_chunk$set(cache = TRUE, warning = FALSE, 
                      message = FALSE)

suppressMessages(library(reshape2))
suppressMessages(library(lubridate))
suppressMessages(library(gridExtra))

suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(ini))
suppressMessages(library(ggplot2))
suppressMessages(library(kableExtra))
suppressMessages(library(knitr))
suppressMessages(library(lubridate))


```


```{r load_data, include=FALSE, cache=TRUE, cache.lazy=FALSE}
load("bios_data_enc_pts_v0.2.RData")
load("bios_data_v0.2.RData")
```

First remove some 40 enc's which are not outpatient from `rar_mg`
```{r only_OUTPATIENT, cache.lazy=FALSE}
tpp <- setdiff(rar_mg$EMPI_DATE, rar_enc$EMPI_DATE)
rar_mg<- rar_mg %>% filter(!(EMPI_DATE %in% tpp))
```


Cumulative en
```{r cumulative_enc}
tmp <- rar_mg %>%
  mutate(age_0 = abs(as.numeric(difftime(ENC_DATE, BIRTH_DATE, units="days"))) < 365,
         Month = paste(year(ENC_DATE), month(ENC_DATE), sep="_"))

tmp %>% 
  group_by(Month) %>%
  summarize(N=n(),
            N_age_0 = sum(age_0, na.rm=T),
            F_age_0 = N_age_0 / n())

# tmp %>%
#   group_by(ENC_DATE) %>%
#   summarise(N=n()) %>%
#   ggplot(.) + geom_point(aes(x=ENC_DATE, y=cumsum(N)/sum(N)))
```

```{r cumulative_enc_70_90}
rar_enc %>% select(ENC_DATE) %>%
  group_by(ENC_DATE) %>%
  summarise(N=n()) %>%
  ggplot(.) + geom_point(aes(x=ENC_DATE, y=cumsum(N)/sum(N))) + 
  xlim(as.POSIXct(c("1970-01-01", "1999-01-01"))) +
  ylim(0, 0.0015)

```


How many enc's ENC_DATE are same as BIRTH_DAY? and how do their data look like?
```{r ENC_BIRTHDAY}
summary(rar_mg %>% 
  filter(ENC_DATE == BIRTH_DATE))
```
37. All the Lab, Dx are missing. So remove them also.

```{r rm_ENC_at_BIRTH}
rar_mg %<>% filter(ENC_DATE != BIRTH_DATE)
```

What is distribution of ENC_DATE - BIRTH_DATE (Age in rar_mg)?
```{r dis_ENC_to_BIRTH}
rar_mg %>% select(ENC_DATE, BIRTH_DATE, Age) %>%
  mutate(Enc_Birth = (ENC_DATE - BIRTH_DATE)/24) %>%
  ggplot(.) + geom_density(aes(Enc_Birth))
```

Encounter to Birthday: Before ENC year 1999
```{r dis_ENC_to_BIRTH_before_1999}
rar_mg %>% select(ENC_DATE, BIRTH_DATE, Age) %>%
  filter(year(ENC_DATE) < 1990) %>%
  mutate(ENC_to_Birth = (ENC_DATE - BIRTH_DATE)/24) %>%
  ggplot(.) + geom_density(aes(Age))
```
this means for Encounters before 1999, most of them were under `r 1500/365` years old when an encouter occurred.  




Now for those between 1970 - 1999:
```{r details_enc, eval=FALSE}
rar_mg %>% filter(ENC_DATE <= as.POSIXct("2000-01-01") & ENC_DATE >= as.POSIXct("1970-01-01"))
```








