---
title: "Find AVS Labs in EPIC data set"
output: 
  html_document:
    theme: journal
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 15
    fig_height: 8
    df_print: paged
---

```{r setup, echo=FALSE}
suppressMessages(library(reshape2))
suppressMessages(library(lubridate))
suppressMessages(library(gridExtra))

suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(ini))
suppressMessages(library(ggplot2))

suppressMessages(library(knitr))
suppressMessages(library(scales))
# suppressMessages(library(reporttools))
# suppressMessages(library(readxl))
# suppressMessages(library(gtools))
source("~/repos/Daniel_Herman_Aldosterone_2017_03/code/R/common_anal/RAR_fxns.R", chdir = TRUE)

```

```{r load_data, include=FALSE, cache=TRUE, cache.lazy=FALSE}
lab_raw <- load_Lab(dat_file = "/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_LABS.csv", 
                    lab_source = "PDS_EPIC",
                    left_censor_date = as.Date("1997-01-01"),
                    adjust_up = 1.5, adjust_down = 0.5, logger=NULL)

lab_raw$EMPI_DATE <- paste(lab_raw$EMPI, as.Date(lab_raw$ENC_DATE))

lab_raw_no_na <- lab_raw %>% filter(!is.na(RESULT_VALUE))
```

# Finding AVS through RESULT_ITEM_CODE

### "adrenal" {-}
```{r adrenal_nm, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("adrenal", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r adrenal}
lab_raw_no_na %>% filter(grepl("adrenal", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```


### "cortisol" {-}
```{r cortisol_nm, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("cortisol", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r cortisol}
lab_raw_no_na %>% filter(grepl("cortisol", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```

### "c lcort","lcort" {-}
```{r cort, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("^c lcort|^lcort", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r cort_n}
lab_raw %>% 
  filter(!is.na(RESULT_VALUE)) %>%
  filter(grepl("^c lcort|^lcort", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```





### "icort"{-}
```{r icort, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("icort", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r icort_n, echo=FALSE}
lab_raw %>% 
  filter(!is.na(RESULT_VALUE)) %>%
  filter(grepl("icort", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```



### "rcort"{-}
```{r rcort, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("rcort", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r rcort_n, echo=FALSE}
lab_raw %>% 
  filter(!is.na(RESULT_VALUE)) %>%
  filter(grepl("rcort", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```


### "avs" {-}
```{r avs_nm}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("avs", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```
None.

### "ivc" {-}
```{r ivc_nm, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("ivc", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r ivc}
lab_raw_no_na %>% filter(grepl("ivc", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```

How many EMPI_DATE?
```{r ivc_distinct}
lab_raw_no_na %>% filter(grepl("ivc", tolower(RESULT_ITEM_CODE))) %>%
  # group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n_distinct(EMPI_DATE)) %>%
  arrange(desc(N))
```


### "left|right" {-}
```{r left_right_nm, echo=FALSE}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("left|right", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r left_right}
lab_raw_no_na %>% filter(grepl("left|right", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```
How many EMPI_DATE?
```{r left_right_distinct}
lab_raw_no_na %>% filter(grepl("left|right", tolower(RESULT_ITEM_CODE))) %>%
  # group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n_distinct(EMPI_DATE)) %>%
  arrange(desc(N))
```

### "aldo" {-}
```{r aldo}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("aldo", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r aldo_nm}
lab_raw_no_na %>% filter(grepl("aldo", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```




### "urine" {-}
```{r urine}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("urine", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```

```{r urine_nm}
lab_raw_no_na %>% filter(grepl("urine", tolower(RESULT_ITEM_CODE))) %>%
  group_by(RESULT_ITEM_CODE) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```
### "cosyntropin" or "infusion" {-}
```{r cosyntropin_infusion_nm}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("cosyntropin|infusion", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```
None.



### "kidney" {-}
```{r kidney_nm}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("kidney", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```





### "adenoma" {-}
```{r adenoma_nm}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("adenoma", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```
None.

### "vein" {-}
```{r vein_nm}
unique(lab_raw$RESULT_ITEM_CODE)[grepl("vein", tolower(unique(lab_raw$RESULT_ITEM_CODE)))]
```
None.


# Paired AVS Tests
Found related AVS Tests: "IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE", "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL", "LCORT", "C LCORT"

## IVC/Right/Left Aldo
```{r aldo_pair}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE")) %>%
  group_by(EMPI_DATE) %>%
  summarise(N = n_distinct(RESULT_ITEM_CODE)) %>% ungroup() %>%
  count(N)
```

```{r nonpaired_aldo, include=FALSE}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE")) %>%  
  group_by(EMPI_DATE) %>%
  filter(n_distinct(RESULT_ITEM_CODE) < 3)  %>%
  select(EMPI_DATE, RESULT_ITEM_CODE,everything()) %>%
  arrange(EMPI_DATE)
```






### At PK_ENCOUNTER_ID Level? {-}
```{r aldo_pk_enc_id, include=FALSE}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("Right Aldos", "Left Aldos", "IVC Aldosterone")) %>%    group_by(PK_ENCOUNTER_ID) %>%
  filter(n_distinct(RESULT_ITEM_CODE) < 3)  %>%
  select(EMPI_DATE, RESULT_ITEM_CODE,everything()) %>%
  arrange(PK_ENCOUNTER_ID)
```
none.

### At EMPI_DATE Level, Duplicate Aldo tests? {-}
```{r dup_aldo, include=FALSE}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("Right Aldos", "Left Aldos", "IVC Aldosterone")) %>%  
  group_by(EMPI_DATE) %>%
  mutate(N_temp=n()) %>%
  summarise(N=max(N_temp), N_dis = n_distinct(RESULT_ITEM_CODE)) %>% ungroup() %>%
  filter(N != N_dis)  %>%
  arrange(EMPI_DATE)
```
none.

## IVC/Right/Left Aldo/Cortisol
If we remove NA result value, only 6 left:
```{r aldo_cortisol_pair_ALL}
lab_raw_no_na %>% 
filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE", "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL", "LCORT", "C LCORT")) %>%  
  # mutate(RESULT_ITEM_CODE = case_when(RESULT_ITEM_CODE %in% c("RCORT", "RIGHT CORTISOL") ~ "RCORT",
  #                                     RESULT_ITEM_CODE %in% c("LCORT", "LEFT CORTISOL") ~ "LCORT",
  #                                     RESULT_ITEM_CODE %in% c("ICORT", "IVC CORTISOL") ~ "ICORT",
  #                                     TRUE ~ RESULT_ITEM_CODE)) %>%
  count(RESULT_ITEM_CODE)
```





### For IVC/Right/Left Aldo/Cortisol, check their RESULT_RESOURCE, UNIT_OF_MEASURE, and RESULT_STATUS
```{r result_status_aldo_cortisol}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE", "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL", "LCORT", "C LCORT")) %>%
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE, UNIT_OF_MEASURE, LOINC_CODE, RESULT_STATUS) %>%
  summarise(N=n())
```
The LOINC_CODE and RESULT_RESOURCE removed:
```{r units_aldo_cortisol_no_loinc}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE", "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL", "LCORT", "C LCORT")) %>%
  group_by(RESULT_ITEM_CODE, UNIT_OF_MEASURE , RESULT_STATUS) %>%
  summarise(N=n())
```
Units are good. 
```{r result_status_avs}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE", "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL", "LCORT", "C LCORT")) %>%
  count(RESULT_STATUS)
```
There are new categories for RESULT_STATUS (with arbitrary ordering): Corrected > Final.






# Urine Aldo [Aldo, Creatinine]
## EPIC:
For EPIC:
For 24HR URINE CREATININE, there are records with unit of 'mg/dL' which is differen from others, so remove them
For 24HR URINE CREATININE, there are records with unit of "g/day" -> change them into "mg/day": remember to change the RESULT_VALUE
For other 3 RESULT_ITEM_CODE, there is no issue for UNITs.   
4 RESULT_ITEM_CODE: "24HR URINE CREATININE", "CRE D ALDOS", "URINE ALDOSTERONE", "ALDOSTERONE, URINE":

```{r urine_aldo, cache.lazy=FALSE}
lab_raw_epic <- load_Lab(dat_file = "/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_LABS.csv", lab_source = "EPIC",
                      left_censor_date = as.Date("1997-01-01"),
                      adjust_up = 1.5, adjust_down = 0.5, logger=logger)
lab_raw_epic_no_na <- lab_raw_epic %>% filter(!is.na(RESULT_VALUE)) %>%  
  mutate(EMPI_DATE = paste(EMPI, as.Date(ENC_DATE)))
  
```

```{r epic_Aldo_Urine, eval=FALSE, include=FALSE}
lab_raw_epic_no_na %>% 
  group_by(PK_ENCOUNTER_ID) %>%
  filter(any(ORDER_ITEM_CODE %in% c("C9009900", "Q19573", "83497A"))) %>% ungroup() %>%
  arrange(PK_ENCOUNTER_ID, PK_ORDER_ID,PK_ORDER_RESULT_ID, RESULT_ITEM_CODE) %>%
  select(EMPI, ENC_DATE, PK_ORDER_ID, ORDER_START_DATE, ORDER_NAME, RESULT_ITEM_CODE, RESULT_VALUE, RESULT_TEXT, UNIT_OF_MEASURE, RESULT_RESOURCE) %>%
  View()
```
Check UNIT_OF_MEASURE, RESULT_RESOURCE, LOINC_CODE:
```{r epic_result_item_code}
lab_raw_epic_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("24HR URINE CREATININE", "CRE D ALDOS", "URINE ALDOSTERONE", "ALDOSTERONE, URINE")) %>%
  # filter(LOINC_CODE != "20624-3" | is.na(LOINC_CODE)) %>%
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE, LOINC_CODE,UNIT_OF_MEASURE)  %>%
  summarise(N = n())
```
So remove units of "mg/dL", in "24HR URINE CREATININE". Also, unify units for "24HR URINE CREATININE":
```{r epic_result_item_Final}
lab_raw_epic_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("24HR URINE CREATININE", "CRE D ALDOS", "URINE ALDOSTERONE", "ALDOSTERONE, URINE")) %>%
  filter(UNIT_OF_MEASURE != "mg/dL" | is.na(UNIT_OF_MEASURE)) %>%
  mutate(RESULT_VALUE = ifelse(RESULT_ITEM_CODE == "24HR URINE CREATININE" & UNIT_OF_MEASURE %in% c("g/24-h", "g/24 h", "G/24HR"),
                               RESULT_VALUE*1000, RESULT_VALUE)) %>%
  mutate(UNIT_OF_MEASURE = case_when(RESULT_ITEM_CODE %in% c("24HR URINE CREATININE", "CRE D ALDOS") ~ "mg/day",
                                     RESULT_ITEM_CODE %in% c("ALDOSTERONE, URINE", "URINE ALDOSTERONE") ~ "ug/day",
                                     TRUE ~ "Unknown")) %>%
  
  group_by(RESULT_ITEM_CODE, UNIT_OF_MEASURE)  %>%
  summarise(N = n())
```

```{r, include=FALSE}
temp <- lab_raw_epic_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("24HR URINE CREATININE", "CRE D ALDOS", "URINE ALDOSTERONE", "ALDOSTERONE, URINE")) %>%
  filter(UNIT_OF_MEASURE != "mg/dL" | is.na(UNIT_OF_MEASURE)) %>%
  mutate(RESULT_VALUE = ifelse(RESULT_ITEM_CODE == "24HR URINE CREATININE" & UNIT_OF_MEASURE %in% c("g/24-h", "g/24 h", "G/24HR"),
                               RESULT_VALUE*1000, RESULT_VALUE)) %>%
  mutate(UNIT_OF_MEASURE = case_when(RESULT_ITEM_CODE %in% c("24HR URINE CREATININE", "CRE D ALDOS") ~ "mg/day",
                                     RESULT_ITEM_CODE %in% c("ALDOSTERONE, URINE", "URINE ALDOSTERONE") ~ "ug/day",
                                     TRUE ~ "Unknown"))
```
That corresponds to: `r length(unique(temp$EMPI_DATE))` unique EMPI_DATE, `r length(unique(temp$EMPI))`

## CERNER
This is some ORDER_ITEM_CODE previously used... just take a look to start:
```{r old_OIC}
lab_raw_no_na %>% filter(ORDER_ITEM_CODE %in% c("C9009900", "Q19573", "83497A")) %>%
  group_by(ORDER_ITEM_CODE, RESULT_ITEM_CODE) %>%
  summarise(N =n()) %>% ungroup() %>% arrange(desc(N))
```
Nothing...

```{r check_Aldo_Urine, eval=FALSE, include=FALSE}
lab_raw_no_na %>% 
  group_by(PK_ENCOUNTER_ID) %>%
  filter(any(RESULT_ITEM_CODE %in% c("U Aldosterone"))) %>% ungroup() %>%
  arrange(PK_ENCOUNTER_ID, PK_ORDER_ID,PK_ORDER_RESULT_ID, RESULT_ITEM_CODE) %>%
  select(EMPI, ENC_DATE, PK_ORDER_ID, ORDER_START_DATE, ORDER_NAME, RESULT_ITEM_CODE, RESULT_VALUE, RESULT_TEXT, UNIT_OF_MEASURE, RESULT_RESOURCE) %>%
  View()
```

Now select 3 labs associated with Aldosterone, Urine:
```{r aldo_urine}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("U Aldosterone", "Cre mg Aldos","Cre D Aldos")) %>%
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE,UNIT_OF_MEASURE, LOINC_CODE)  %>%
  summarise(N = n())
```



Picking 2 RESULT_ITEM_CODE: "U Aldosterone", "Cre D Aldos"
### Impute NA UNIT_OF_MEASURE and unify UNITS {-}
Since we focus on those 2 RESULT_ITEM_CODE, now remove the restriction for ORDER_ITEM_CODE:
```{r reorganize_result_item_code}
lab_raw_no_na %>% 
  # group_by(PK_ENCOUNTER_ID) %>%
  # filter(any(ORDER_ITEM_CODE %in% c("C9009900", "Q19573", "83497A"))) %>% ungroup() %>%
  filter(RESULT_ITEM_CODE %in% c("U Aldosterone","Cre D Aldos")) %>%
  # filter(LOINC_CODE != "20624-3" | is.na(LOINC_CODE)) %>%
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE,UNIT_OF_MEASURE)  %>%
  summarise(N = n())
```

```{r unify_units}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("U Aldosterone","Cre D Aldos")) %>%
  mutate(UNIT_OF_MEASURE = ifelse(RESULT_ITEM_CODE == "U Aldosterone", "ug/day", UNIT_OF_MEASURE)) %>% 
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE,UNIT_OF_MEASURE)  %>%
  summarise(N = n())
```

Take a look at their RESULT_STATUS:
```{r result_status}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("U Aldosterone","Cre D Aldos")) %>%
  mutate(UNIT_OF_MEASURE = ifelse(RESULT_ITEM_CODE == "U Aldosterone", "ug/day", UNIT_OF_MEASURE)) %>% 
  group_by(RESULT_ITEM_CODE, RESULT_RESOURCE,UNIT_OF_MEASURE, RESULT_STATUS)  %>%
  summarise(N = n())
```
There are two RESULT_STATUS: Corrected, Verified:
```{r echo=FALSE, eval=FALSE}
lab_raw_no_na %>% 
  filter(RESULT_ITEM_CODE %in% c("U Aldosterone","Cre D Aldos")) %>%
  mutate(UNIT_OF_MEASURE = ifelse(RESULT_ITEM_CODE == "U Aldosterone", "ug/day", UNIT_OF_MEASURE)) %>% 
  group_by(EMPI_DATE) %>%
  filter(n_distinct(RESULT_STATUS) > 1) %>% ungroup() %>%
  arrange(EMPI_DATE,RESULT_ITEM_CODE, RESULT_RESOURCE,UNIT_OF_MEASURE, RESULT_STATUS)  %>%
  View()
```
This returns nothing, which means for one EMPI_DATE, there is only one RESULT_STATUS.
