---
title: "AVS Lab Test vs RDB"
output: 
  html_document:
    theme: journal
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 15
    fig_height: 8
    df_print: paged
---

```{r setup, echo=FALSE}
suppressMessages(library(reshape2))
suppressMessages(library(lubridate))
suppressMessages(library(gridExtra))

suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(ini))
suppressMessages(library(ggplot2))
suppressMessages(library(data.table))
suppressMessages(library(knitr))
suppressMessages(library(scales))

# suppressMessages(library(reporttools))
# suppressMessages(library(readxl))
# suppressMessages(library(gtools))
# source("~/repos/Daniel_Herman_Aldosterone_2017_03/code/R/common_anal/RAR_fxns.R", chdir = TRUE)

```

# Load and Modify
```{r load_data, include=FALSE, cache=TRUE, cache.lazy=FALSE}
load("/data/processed_data/RAR/bios_data_enc_pts_v0.2.3.RData")
```

For AVS and UAldo indicator, change NA to FALSE. Also add them in enc level:
```{r NA_to_F, cache.lazy=FALSE}
pts[is.na(pts$AVS_indicator), "AVS_indicator"] <- FALSE
pts[is.na(pts$UAldo_indicator), "UAldo_indicator"] <- FALSE
```


# AVS
```{r overall}
table(pts$AVS_indicator)
```

```{r avs_year_2}
table(pts$AVS_indicator, year(pts$AVS_first_DATE))
```
AVS Lab Tests starts in 2008.

```{r n_avs}
rar_mg %>% group_by(EMPI) %>%
  summarise(N_AVS = sum(AVS_indicator)) %>%
  count(N_AVS)
```


```{r n_ualdo}
rar_mg %>% group_by(EMPI) %>%
  summarise(N_UAldo = sum(UAldo_indicator)) %>%
  count(N_UAldo)
```


# AVS & RDB
```{r avs_rdb}
table(pts$AVS_indicator, pts$PA_AVS_tot_0115)
```
For the patients who had AVS Tests:
```{r avs_year}
table(pts$AVS_indicator, pts$PA_AVS_tot_0115, year(pts$AVS_first_DATE))
```
For the patients who had AVS Tests:
```{r bp_year}
table(pts$AVS_indicator, pts$PA_AVS_tot_0115, year(pts$first_ENC_DATE))
```

## AVS but not RDB
```{r AVS_notRDB_year}
table(pts$AVS_indicator & !pts$PA_AVS_tot_0115 & year(pts$first_ENC_BP_DATE) < 2015)
```

```{r AVS_notRDB_by_year}
table(pts$AVS_indicator & !pts$PA_AVS_tot_0115, year(pts$first_ENC_BP_DATE))
```

Find out these patients
```{r AVS_notRDB_lst, include=FALSE, eval=FALSE}
pts %>% filter(AVS_indicator & !PA_AVS_tot_0115) %>% 
  # arrange(desc(year(first_ENC_BP_DATE))) %>%
  filter(year(first_ENC_BP_DATE) == 2014) %>%
  View()

```


## not AVS but RDB
```{r not_AVS_RDB}
table(!pts$AVS_indicator & pts$PA_AVS_tot_0115, year(pts$first_ENC_BP_DATE))
```


Find out these patients
```{r not_AVS_RDB_lst, include=FALSE, eval=FALSE}
pts %>% filter(!AVS_indicator & PA_AVS_tot_0115) %>% 
  # arrange(desc(year(first_ENC_BP_DATE))) %>%
  filter(year(first_ENC_BP_DATE) == 2010) %>%
  View()

```


```{r read_raw, include=FALSE, echo=FALSE}
colClasses_E <- c(ENC_DATE = "PDS_DateTime", ORDER_START_DATE = "PDS_DateTime", O_SOURCE_LAST_UPDATE = "PDS_DateTime", 
                    RESULT_DATE = "PDS_DateTime", 
                    EMPI = 'character', PK_ENCOUNTER_ID = 'character', PK_ORDER_ID = 'character', ORDER_NAME = 'character', 
                    ORDER_ITEM_CODE = 'character', PK_ORDER_RESULT_ID = 'character', RESULT_VALUE = 'character',
                    UNIT_OF_MEASURE = 'character', RESULT_STATUS = 'character', RESULT_ITEM_CODE = 'character', 
                    ORDERING_PROV = 'character', HAR_NUMBER = 'character', 
                    ORDER_GROUP = 'character', RESULT_TEXT = 'character', RESULT_RESOURCE = "character", 
                    ORES_SOURCE_LAST_UPDATE = "PDS_DateTime", LOINC_CODE = 'character')

colClasses_C <-  c(ENC_DATE = "PDS_DateTime", ORDER_START_DATE = "PDS_DateTime", O_SOURCE_LAST_UPDATE = "PDS_DateTime", 
                    RESULT_DATE = "PDS_DateTime", 
                    EMPI = 'character', PK_ENCOUNTER_ID = 'character', PK_ORDER_ID = 'character', ORDER_NAME = 'character', 
                    ORDER_ITEM_CODE = 'character', PK_ORDER_RESULT_ID = 'character', RESULT_VALUE = 'character',
                    UNIT_OF_MEASURE = 'character', RESULT_STATUS = 'character', RESULT_ITEM_CODE = 'character', 
                    HAR_NUMBER = 'character', 
                    ORDER_GROUP = 'character', RESULT_TEXT = 'character', RESULT_RESOURCE = "character", 
                    ORES_SOURCE_LAST_UPDATE = "PDS_DateTime", LOINC_CODE = 'character')


lab_epic <- fread("/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_LABS.csv", stringsAsFactors=F, colClasses = colClasses_E)
lab_cerner <- fread("/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_LABSC.csv", stringsAsFactors=F, colClasses = colClasses_C)

empi <- pts %>% 
  filter(!AVS_indicator & PA_AVS_tot_0115) %>%
  pull(EMPI) # 119

ric <- unique(lab_epic$RESULT_ITEM_CODE)



lab_epic <- as.tibble(lab_epic)
lab_epic %>% 
  filter(EMPI %in% empi) %>%
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE",
                                 "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL")) %>%
  group_by(EMPI) %>%
  count(EMPI) # 8


lab_epic %>% 
  # filter(EMPI %in% empi) %>%
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE",
                                 "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL")) %>%
  group_by(EMPI) %>%
  count(EMPI) # 441


```

What are the distribution of year from EPIC?
```{r epic}
lab_epic %>% 
  filter(EMPI %in% empi) %>%
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE",
                                 "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL")) %>%
  group_by(EMPI) %>%
  summarise(Year = mean(year(ENC_DATE))) %>%
  count(Year)
```



For those 165 - 54 = 111 patients, why both EPIC and CERNER did not catch them?
```{r get_pts_not_PDS_EPIC_CERNER, eval=FALSE}
empi_none <- setdiff(empi, lab_epic %>% 
  filter(EMPI %in% empi) %>%
  filter(RESULT_ITEM_CODE %in% c("IVC ALDOSTERONE", "IVC CORTISOL", "LEFT ALDOSTERONE",
                                 "LEFT CORTISOL", "RIGHT ALDOSTERONE", "RIGHT CORTISOL")) %>%
  group_by(EMPI) %>%
  pull(EMPI))
```

(1) Could they be found in PDS directly?
Yes, but not for those 6 tests
(2) Do they show in EPIC?
Among those chart-reviewed, only found 1 with "AVS" in Progress Note. All of them had no AVS labs; some of them had no labs at all -- are they not our patients?


# AVS or RDB
```{r avs_or_rdb}
table(pts$AVS_indicator, pts$PA_AVS_tot_0115)
```
So from this table, if RDB only, there will be `r sum(pts$PA_AVS_tot_0115)` out of `r nrow(pts)`, `r percent(sum(pts$PA_AVS_tot_0115)/nrow(pts))`. Once we added AVS in, there will be ADDITIONAL `r nrow(pts[(!pts$PA_AVS_tot_0115) & pts$AVS_indicator,])` patients, then the total would be `r nrow(pts[(pts$PA_AVS_tot_0115) | pts$AVS_indicator,])`, `r percent(nrow(pts[(pts$PA_AVS_tot_0115) | pts$AVS_indicator,])/nrow(pts))`.

