---
title: "Lab_PK_OID_RIC"
output: html_document
---

```{r}
library(ini)
config <- read.ini("../../config.ini")

# set directory
working_dir <- paste(config$Directories$repos_dir, config$Directories$working_dir_suffix, sep = "/")

output_dir <- paste(config$Directories$repos_dir, config$Directories$output_dir_suffix, sep = "/")
out_root <- config$RAR$out_root

# set working directory
setwd(working_dir)

```


```{r setup, include=FALSE, cache=TRUE, root.dir=working_dir}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = working_dir)
library(dplyr)
library(data.table)
library(tibble)
suppressMessages(library(tidyr))
setwd(working_dir)
source("../../common_anal/RAR_fxns.R", chdir = TRUE)

```

## Labs
### Collapse into PK_ORDER_ID + RESULT_ITEM_CODE level
Read in labs
```{r load_lab, cache=TRUE}
rar_lab <- load_Lab(dat_file = "/data/raw_data/PA/HERMANDA_RAR_PTS_LABS.csv", lab_source = "ALL", adjust_up = 1.5, adjust_down = 0.5)
nrow(rar_lab) == length(unique(rar_lab$PK_ORDER_RESULT_ID)) # FALSE
```

Check what is duplicated for PK_ORDER_RESULT_ID
```{r, cache=TRUE, dependson=c("load_lab")}
temp <- duplicated(rar_lab$PK_ORDER_RESULT_ID)
head(which(temp))

rar_lab[5420305:5420310,] %>% print.data.frame()
# NA's in PK_ORDER_RESULT_ID
sum(!is.na(rar_lab[which(is.na(rar_lab$PK_ORDER_RESULT_ID)), "RESULT_VALUE"])) # 0


```
This means that those with NA PK_ORDER_RESULT_ID all have a missing RESULT_VALUE. So remove them.

```{r, cache=TRUE, dependson=c("load_lab")}
dat <- rar_lab
nrow(dat) == length(unique(dat$PK_ORDER_RESULT_ID))
```
Now, PK_ORDER_ID could be unique ID



Include RAR, POTASSIUM, and top 44 most common lab tests
```{r, cache=TRUE, dependson=c("load_lab")}
dat %<>% filter(!is.na(dat$PK_ORDER_RESULT_ID))

# Create new ENC ID: EMPI_DATE
dat$EMPI_DATE <- paste(dat$EMPI, format(dat$ENC_DATE, "%Y-%m-%d"))

# Create ret table
ret <- as.tibble()

# RAR
## catch "ALDO"|"RENIN"
dat_rar <- dat %>% filter(grepl("renin|aldo", tolower(RESULT_ITEM_CODE))) %>%
  group_by(ORDER_ITEM_CODE, RESULT_ITEM_CODE)

## Exclude ORDER_ITEM_CODE that are for AVS or urine specimens
dat_rar %<>% filter(!(ORDER_ITEM_CODE %in%  c("C9009900", "C9009995", "C9009997", "Q19573", "83497A")))


## dropped many rows here
ret <- dat_rar %>% 
  filter(RESULT_ITEM_CODE %in% c("RENIN ACTIVITY","RENIN", "PLASMA RENIN ACTIVITY, LC/MS/MS", "PLASMA RENIN ACTIVITY")) %>%
  mutate(Test = "PRA")


ret <- dat_rar %>% 
  filter(RESULT_ITEM_CODE %in% c("DIRECT RENIN")) %>% 
  mutate(Test = "DRC") %>%
  rbind(., ret)

ret <- dat_rar %>% 
  filter(RESULT_ITEM_CODE %in% c("ALDOSTERONE, SERUM", "ALDOSTERONE, LC/MS/MS", "ALDOSTERONE")) %>%
  mutate(Test = "Aldo") %>%
  rbind(., ret)

ret %<>% ungroup()


ret <- dat  %>% filter(RESULT_ITEM_CODE == "POTASSIUM") %>% 
          mutate(Test = "POTASSIUM") %>%
          rbind(., ret)



num_labs <- 44

ric_ranked_lt <- dat %>% group_by(RESULT_ITEM_CODE) %>%
    summarise(N = n()) %>%
    arrange(desc(N)) %>%
    na.omit(.) %>%
    filter(!(RESULT_ITEM_CODE %in% c("POTASSIUM") | RESULT_ITEM_CODE %in% dat_rar$RESULT_ITEM_CODE))
  
  # num_labs = 44 for CBC (Complete Blood Count) & CMP (Comprehensive Metabolic Panel)
  ric_lt <- ric_ranked_lt[1:num_labs,]
  
  ret <- dat %>% filter(RESULT_ITEM_CODE %in% ric_lt$RESULT_ITEM_CODE) %>%
          mutate(Test = RESULT_ITEM_CODE) %>%
          rbind(., ret)
  
length(unique(ret$PK_ORDER_ID))
ret$oid_ric <- paste(ret$PK_ORDER_ID, ret$RESULT_ITEM_CODE, sep = "_")
length(unique(ret$oid_ric)) # result will have 3763013 rows
```


Get duplicated oid_ric
```{r, cache=TRUE, dependson=c("load_lab")}
dups <- ret[which(duplicated(ret$oid_ric)), "oid_ric"]
```


```{r, cache=TRUE, dependson=c("load_lab")}
r0 <- ret %>% filter(oid_ric %in% dups$oid_ric) %>% arrange(oid_ric)


# list for those have only one RESULT_STATUS
tp <- r0 %>% group_by(oid_ric) %>% summarise(N = n_distinct(RESULT_STATUS)) %>% filter(N == 1)
# For them, see what is the difference except for PK_ORDER_RESULT_ID


r0 %>% filter(oid_ric %in% tp$oid_ric) %>% group_by(oid_ric) %>% select(-PK_ORDER_RESULT_ID) %>% summarise(N_d = n_distinct(RESULT_VALUE)) %>%
  arrange(desc(N_d))

r0 %>% filter(oid_ric == "2394114570_ALT") %>% mutate_at(vars(RESULT_VALUE), funs(median(., na.rm = TRUE))) %>% print.data.frame()
```


Apply:
```{r, cache=TRUE, dependson=c("load_lab")}
ret$RESULT_STATUS <- factor(ret$RESULT_STATUS, levels = c("Corrected", "Final", "Preliminary", "Incomplete", NA))
temp <- ret %>% group_by(PK_ORDER_ID, RESULT_ITEM_CODE) %>%
          arrange(RESULT_STATUS) %>% mutate_at(vars(RESULT_VALUE), funs(median(., na.rm = TRUE))) %>% slice(1) 
          
  
```

Quality Checking
```{r, cache=TRUE, dependson=c("load_lab")}
length(unique(temp$oid_ric)) # The number matches the UNIQUE OID_RIC
```
QC - "2393819447_INR"
```{r, cache=TRUE, dependson=c("load_lab")}
print.data.frame(temp %>% filter(oid_ric == "2393819447_INR"))
print.data.frame(subset(temp, oid_ric == "2393874016_# LYMPHOCYTES"))
```
Not correct... for oid_ric which has multiple levels in RESULT_STATUS, should only pick the higher level.   


Another Approach:
Separate ret into two groups: oid_ric has only one record; oid_ric has multitple records
```{r, cache=TRUE, dependson=c("load_lab")}
r0 <- subset(ret, !(oid_ric %in% dups$oid_ric))
r1 <- subset(ret, oid_ric %in% dups$oid_ric)

r1 %<>%
  group_by(oid_ric, RESULT_STATUS) %>%
  mutate_at(vars(RESULT_VALUE), funs(median(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(oid_ric) %>%
  arrange(RESULT_STATUS) %>%
  slice(1)
```
