---
title: "Lab to EMPI_DATE"
output: html_document
---

```{r}

```

```{r}
library(ini)
config <- read.ini("~/repos/Daniel_Herman_Aldosterone_2017_03/code/R/PA_analysis/Biostat_process/config.ini")

# set directory
working_dir <- paste(config$Directories$repos_dir, config$Directories$working_dir_suffix, sep = "/")

output_dir <- paste(config$Directories$repos_dir, config$Directories$output_dir_suffix, sep = "/")
out_root <- config$RAR$out_root

```


```{r setup, include=FALSE, cache=TRUE, root.dir=working_dir}
knitr::opts_chunk$set(echo = TRUE)
opts_knit$set(root.dir = working_dir)
library(dplyr)
library(data.table)
library(tibble)
suppressMessages(library(tidyr))
setwd(working_dir)
source("common_anal/RAR_fxns.R")

```


### Collapse into EMPI_DATE level
```{r load_lab, cache=TRUE}
lab_raw <- load_Lab(dat_file = "/data/raw_data/PA/HERMANDA_RAR_PTS_LABS.csv", lab_source = "ALL",
                    adjust_up = 1.5, adjust_down = 0.5)

lab <- clean_Lab(dat = lab_raw, RAR_only = FALSE, potassium_in = TRUE,
                         num_labs=44)

```
temp is in PK_ORDER_ID + RESULT_ITEM_CODE level. Next step is to collapse it into EMPI_DATE level.


Use previous function to deal with RAR Labs
```{r RAR-labs, cache=TRUE, dependson=c("load_lab")}
rar_lab <- subset(lab, Test %in% c("PRA", "DRC", "Aldo"))
rar_lab_collapse <- collapse_RAR_Lab(dat=rar_lab, EMPI_DATE_Level = TRUE)
```


For other labs
```{r gen-other, cache=TRUE, dependson=c("load_lab", "RAR-labs")}
other_lab <- subset(lab, !(Test %in% c("PRA", "DRC", "Aldo")))
nrow(other_lab) # 3746487 rows: PK_ORDER_ID + RIC
length(unique(other_lab$Test)) # 45 other lab tests
length(unique(other_lab$EMPI_DATE)) # 159455 unique EMPI_DATE
```

```{r ID_for-other, dependson=c("load_lab", "RAR-labs", "gen-other")}
temp <- paste(other_lab$EMPI_DATE, other_lab$RESULT_ITEM_CODE)
length(unique(temp)) # 2856910 - Goal for other_lab_EMPI_DATE_RIC
```
This means that for some EMPI_DATE, there are some multiple same tests taken. So split:

```{r New_ID, cache=TRUE, dependson=c("load_lab")}
# create a new temporary ID: EMPI_DATE + RESULT_ITEM_CODE
other_lab$EMPI_DATE_RIC <- paste(other_lab$EMPI_DATE, other_lab$RESULT_ITEM_CODE)
dups <- other_lab[duplicated(other_lab$EMPI_DATE_RIC), 'EMPI_DATE_RIC']
r0 <- subset(other_lab, !(EMPI_DATE_RIC %in% dups$EMPI_DATE_RIC))
r1 <- subset(other_lab, EMPI_DATE_RIC %in% dups$EMPI_DATE_RIC)
length(unique(r1$EMPI_DATE_RIC))  # 199134 - Goal for r1


tpp <- paste(other_lab$EMPI_DATE_RIC, other_lab$PK_ORDER_ID)

sum(duplicated(tpp)) # 0
```

The sum equal to 0, which means in each EMPI_DATE_RIC, there is only one PK_ORDER_ID.   
Do another check on ORDER_START_DATE
```{r EMPI_DATE_RIC_OSD, cache=TRUE, dependson=c("load_lab")}
tpp2 <- paste(r1$EMPI_DATE_RIC, r1$ORDER_START_DATE)
sum(duplicated(tpp2))
```
For this combination, there are duplicates.

```{r check-dups, cache=TRUE, dependson=c("load_lab")}
head(tpp2[duplicated(tpp2)])
r1$temp <- paste(r1$EMPI_DATE_RIC, r1$ORDER_START_DATE)

r1 %>% filter(temp == "1001377480 1999-03-27 ALKALINE PHOSPHATASE 1999-03-27 07:16:00") %>% print.data.frame()
```
The result shows that the same test was performed from different order: LIVER FUNCTIONAL PANEL & CMP. --> Take the median
```{r median-for-same-test, cache=TRUE, dependson=c("load_lab")}
temp <- r1 %>% group_by(EMPI_DATE_RIC, ORDER_START_DATE) %>% mutate_at(vars(RESULT_VALUE), funs(median(., na.rm=TRUE))) %>% slice(1)

nrow(temp) + sum(duplicated(tpp2)) == nrow(r1)
```
The TRUE result means now for r1, EMPI_DATE_RIC + ORDER_START_DATE is unique. Now, select by count of ORDER_START_DATE (then arbitrary PK_ORDER_ID) for each EMPI_DATE:
```{r apply-to-r1, cache=TRUE, dependson=c("load_lab")}
r1 %<>% group_by(EMPI_DATE_RIC, ORDER_START_DATE) %>% mutate_at(vars(RESULT_VALUE), funs(median(., na.rm=TRUE))) %>% slice(1)

r1$EMPI_DATE_OSD <- paste(r1$EMPI_DATE, r1$ORDER_START_DATE)
temp <- r1 %>% group_by(EMPI_DATE_OSD) %>% summarize(N=n()) %>% ungroup() %>% full_join(., r1, by = "EMPI_DATE_OSD") %>% group_by(EMPI_DATE_RIC) %>% arrange(desc(N), desc(PK_ORDER_ID)) %>% slice(1)

nrow(temp) == 199134
```
The result is TRUE, which means now the data is on EMPI_DATE_RIC level.
```{r r1, cache=TRUE, dependson=c("load_lab")}
r1 <- temp
```



Combine back r0 and r1. Then Spread into EMPI_DATE table. Since unit of measure is also important, combine it with Test
```{r merge-r0-r1, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE_RIC <- r0 %>% bind_rows(., r1)

length(unique(other_lab_EMPI_DATE_RIC$EMPI_DATE_RIC)) == length(unique(other_lab$EMPI_DATE_RIC))
# other_lab_EMPI_DATE_RIC$Test <- paste(other_lab_EMPI_DATE_RIC$Test, other_lab_EMPI_DATE_RIC$UNIT_OF_MEASURE, sep = "_")
```
TRUE: cleaning does not cause loss in EMPI_DATE date


#### Harmonize Unites
```{r units, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE_RIC %>% group_by(RESULT_ITEM_CODE, UNIT_OF_MEASURE) %>% summarize(N = n()) %>% print.data.frame()
```
Harmonize units: for now, only select the highest count one for each RESULT_ITEM_CODE
```{r harmonize-units, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE_RIC$RIC_units <- paste(other_lab_EMPI_DATE_RIC$RESULT_ITEM_CODE, other_lab_EMPI_DATE_RIC$UNIT_OF_MEASURE)

RIC_units_select <- other_lab_EMPI_DATE_RIC %>% group_by(RESULT_ITEM_CODE, UNIT_OF_MEASURE) %>% summarise(N = n()) %>% arrange(desc(N)) %>% slice(1)

print.data.frame(RIC_units_select)

```
Some units are NA:
```{r NA-units, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE_RIC %>% filter(RESULT_ITEM_CODE == "ANION GAP" | RESULT_ITEM_CODE == "INR") %>% group_by(RESULT_ITEM_CODE,UNIT_OF_MEASURE) %>% summarise(mean = mean(RESULT_VALUE, na.rm=T), min = min(RESULT_VALUE, na.rm=T), max = max(RESULT_VALUE, na.rm=T),N = n()) %>% print.data.frame()
```
NOTE: for ANION GAP, the range seems okay. But for INR, the range (should be around 1 ~ 5) is strange... but the N is siginificantly high, so just keep it now.   
Based on RIC_units_select, select from other_lab_EMPI_DATE_RIC:
```{r select-units, cache=TRUE, dependson=c("load_lab")}
RIC_units_select$RIC_unit <- paste(RIC_units_select$RESULT_ITEM_CODE, RIC_units_select$UNIT_OF_MEASURE)
other_lab_EMPI_DATE_RIC %<>% filter(RIC_units %in% RIC_units_select$RIC_unit) %>% ungroup()

other_lab_EMPI_DATE_RIC %>% group_by(RESULT_ITEM_CODE, UNIT_OF_MEASURE) %>% summarize(N = n()) %>% print.data.frame()
```
Now the units are unique for each RESULT_ITEM_CODE.

Remove cols to spread:
```{r, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE_RIC$Test <- paste(other_lab_EMPI_DATE_RIC$Test, other_lab_EMPI_DATE_RIC$UNIT_OF_MEASURE, sep = "_")
other_lab_EMPI_DATE_RIC %<>% select(EMPI_DATE, Test, RESULT_VALUE)

other_lab_EMPI_DATE <- other_lab_EMPI_DATE_RIC %>% spread(., key = Test, value = RESULT_VALUE, sep = "_")

nrow(other_lab_EMPI_DATE) < length(unique(other_lab$EMPI_DATE))
```
It is less than EMPI_DATE in other_lab, because some are lost in picking units step, but not so many of them.   

Should add EMPI and ENC_DATE back
```{r re-assign-EMPI-Date, cache=TRUE, dependson=c("load_lab")}
other_lab_EMPI_DATE$EMPI <- substr(other_lab_EMPI_DATE$EMPI_DATE, 1, 10)
other_lab_EMPI_DATE$ENC_DATE <- as.Date(substr(other_lab_EMPI_DATE$EMPI_DATE, 12, 21), format = "%Y-%m-%d")
```

To make rar_lab_collapse compatible with other_lab_EMPI_DATE, remove/refine columns in rar_lab_collapse:
```{r, cache=TRUE, dependson=c("load_lab")}
rar_lab_collapse %<>% select(-c(PK_ENCOUNTER_ID, ORDER_START_DATE))
rar_lab_collapse$ENC_DATE <- as.Date(rar_lab_collapse$ENC_DATE)
```

Merge rar_lab_collapse and other_lab_EMPI_DATE:
```{r merge, cache=TRUE, dependson=c("load_lab")}
temp_EMPI_DATE <- append(rar_lab_collapse$EMPI_DATE, other_lab_EMPI_DATE$EMPI_DATE)
length(unique(temp_EMPI_DATE)) # 161330
temp <- full_join(rar_lab_collapse, other_lab_EMPI_DATE, by = "EMPI_DATE")
nrow(temp)
```
Lost some, but not so many!


