---
title: "Distances between ZIPs"
output: 
  html_document:
    theme: journal
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 15
    fig_height: 8
    df_print: paged
---

```{r setup, echo=FALSE}
suppressMessages(library(reshape2))
suppressMessages(library(lubridate))
suppressMessages(library(gridExtra))

suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(ini))
suppressMessages(library(ggplot2))

suppressMessages(library(knitr))
suppressMessages(library(scales))
suppressMessages(library(ggmap))
# suppressMessages(library(reporttools))
# suppressMessages(library(readxl))
# suppressMessages(library(gtools))
source("~/repos/Daniel_Herman_Aldosterone_2017_03/code/R/common_anal/RAR_fxns.R", chdir = TRUE)

```

# ZIP Code in Demo
```{r load_demo_data, include=FALSE, cache=TRUE, cache.lazy=FALSE}

## Patient Demo
rar_demo <- load_RAR_PtDemo(dat_file = "/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_DEMO.csv", logger = NULL)

```
Any patients have multiple ZIP's?
```{r raw_demo_zips}
rar_demo_raw <- fread("/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_DEMO.csv", stringsAsFactors = FALSE)
rar_demo_raw %>% group_by(EMPI) %>%
  summarise(N= n_distinct(ZIP)) %>%
  filter(N > 1)

```
Actually, there are only 3 patients who have multiple ZIP codes, and they have at most 2. Thus, we could ignore them, and use the original algorithm for demo.

```{r demo_zip_NA}
rar_demo %>% filter(ZIP %in% c("", "00000"))
```

For those with "00000" as zip codes, put them as NA.
```{r use_NA}
rar_demo %<>% mutate(ZIP = ifelse(ZIP == "00000", NA, ZIP))
```
Unique ZIP codes in Patient Demo:
```{r demo_unique_zip}
length(unique(rar_demo$ZIP))
```


# ZIP in ENC
```{r load_enc_data, include=FALSE, cache=TRUE, cache.lazy=FALSE}
rm(rar_demo_raw)
## Patient Demo
rar_enc <- load_RAR_enc(dat_file = "/data/raw_data/PA/RAR_v0.2.3/DINGXI_RAR_PTS_ENC.csv", 
                        bp_only = FALSE, EMPI_DATE_Level = TRUE, outpatient_only = TRUE, logger = NULL)

```
NA's? 00000? ""?
```{r check_NA}
table(rar_enc$MASTER_LOCATION_ZIP, useNA = 'always')
```

Get MASTER_LOCATION_CODE ~ ZIP only table:
```{r tb}
enc_zip <- rar_enc %>% select(MASTER_LOCATION_CODE, MASTER_LOCATION_DESCRIPTION, MASTER_LOCATION_ZIP)
# remove dups
enc_zip <- enc_zip[!duplicated(enc_zip),]
sum(is.na(enc_zip$MASTER_LOCATION_ZIP))
```

Impute ZIP bu MASTER_LOCATION_CODE:
```{r try_impute}
temp <- enc_zip %>% group_by(MASTER_LOCATION_DESCRIPTION) %>%
  arrange(MASTER_LOCATION_ZIP) %>%
  mutate(new_zip = MASTER_LOCATION_ZIP[1])
sum(is.na(temp$MASTER_LOCATION_ZIP))
```

Also checked MASTER_LOCATION_ADDRESS_1, MASTER_LOCATION_ADDRESS_2, MASTER_LOCATION_CITY on PDS, they are all missing when ZIP is missing: which means these 3 info will not help on imputing NA ZIP's.

## How Many LOC's, and how many missing?
```{r number_loc}
length(unique(rar_enc$MASTER_LOCATION_CODE))
```
```{r n_missing}
rar_enc %>% group_by(MASTER_LOCATION_CODE) %>%
  filter(all(is.na(MASTER_LOCATION_ZIP))) %>%
  summarise(N = n()) %>%
  arrange(desc(N))
```
There are 1252 out of 1336 master locations (MASTER_LOCATION_CODE) that have missing ZIP's. These 1252 missing ZIP's in MASTER_LOCATION_CODE account for `r percent(sum(is.na(rar_enc$MASTER_LOCATION_ZIP))/nrow(rar_enc))` of encounters.

```{r n_missing_check}
rar_enc %>% group_by(MASTER_LOCATION_ENTITY, MASTER_LOCATION_CODE, MASTER_LOCATION_DESCRIPTION) %>%
  filter(all(is.na(MASTER_LOCATION_ZIP))) %>%
  ungroup() %>%
  select(MASTER_LOCATION_ENTITY, MASTER_LOCATION_CODE, MASTER_LOCATION_DESCRIPTION) %>%
  distinct()

```

```{r output_zip_service,eval=FALSE, include=FALSE}
rar_enc %>% group_by(MASTER_LOCATION_ENTITY, MASTER_LOCATION_CODE, MASTER_LOCATION_DESCRIPTION) %>%
  filter(all(is.na(MASTER_LOCATION_ZIP))) %>%
  summarise(N=n()) %>%
  write.csv(., file="missing_zips.csv", row.names = F)


rar_enc %>% group_by(SERVICE_MASTER_CODE, SERVICE_MASTER_DESCRIPTION) %>%
  summarise(N = n()) %>%
  write.csv(., file="service.csv", row.names=F)
```



# Distances Between Patient ZIP and 19104
There are `r length(unique(rar_demo$ZIP))` unique ZIP codes in patients.
```{r dis}
pts_zip <- data.frame(pt_zip = unique(rar_demo$ZIP), loc_zip="19104")

write.csv(pts_zip, file="zip.csv", row.names=F)

tmp <- mapdist(from = as.character(pts_zip$pt_zip), to = as.character(pts_zip$loc_zip), mode="driving")
```



```{r}
pts_zip$pt_zip[(grepl("^0", pts_zip$pt_zip))]
```



